%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-6pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-7pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-3pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Fanyi Pu} \\ \vspace{1pt}
    \small \faPhone \ \texttt{+65 8398-1454} $|$
    \href{mailto:FPU001@e.ntu.edu.sg}{\faEnvelope \ \underline{\texttt{FPU001@e.ntu.edu.sg}}} $|$
    \href{https://pufanyi.github.io}{\faGlobe \ \underline{\texttt{pufanyi.github.io}}} $|$
    \href{https://scholar.google.com/citations?user=58tv6skAAAAJ}{\faGoogle \ \underline{\texttt{58tv6skAAAAJ}}} $|$ \href{https://github.com/pufanyi}{\faGithub \ \underline{\texttt{pufanyi}}}
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Nanyang Technological University}{Singapore}
      {Bachelor of Computing in Data Science and Artificial Intelligence}{2022 -- 2026}
      \resumeItemListStart
      \resumeItem{Expected Honours (Highest Distinction), Current CGPA: 4.63 / 5.00}
      \resumeItem{Core courses: Data Structure and Algorithms, Probability and Statistics, Regression Analysis, Machine Learning, Software Engineering, Computational Economics, Stochastic Process, Numerical Analysis, Cryptography.}
      \resumeItemListEnd
    \resumeSubheading
      {University of California, Berkeley}{Berkeley, CA}
      {Summer Session}{Jun 2024 -- Aug 2024}
      \resumeItemListStart
      \resumeItem{Studied \textit{Computer Security} and \textit{Game Theory}}
      \resumeItem{GPA: 4.00 / 4.00}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Research Assistant}{Jan 2025 -- May 2025}
      {MMLab@NTU}{Singapore}
      \resumeItemListStart
        \resumeItem{Focused on multimodal understanding of large models.}
        \resumeItem{Currently 900+ citations on Google Scholar.}
      \resumeItemListEnd

    \resumeSubheading
      {The International Collegiate Programming Contest (ICPC)}{2021 -- 2024}
      {Nanyang Technological University / Dalian University of Technology}{Singapore / China}
      \resumeItemListStart
        \resumeItem{Ranked 22th in 2024 ICPC Asia Pacific Championship.}
        \resumeItem{Ranked 13th in 2023 ICPC Asia Jakarta Regional Contest.}
        \resumeItem{Ranked 6th in 2022 ICPC Asia Manila Regional Contest.}
        \resumeItem{Gold medal in 2021 ICPC Asia Kunming Regional contest.}
        \resumeItem{Silver medal in 2021 ICPC Asia Nanjing Regional contest.}
      \resumeItemListEnd

    \resumeSubheading
      {Simon Marais Mathematics Competition}{Dec 2022}
      {Nanyang Technological University}{Singapore}
      \resumeItemListStart
        \resumeItem{Best-in-University Prize in Nanyang Technological University.}
        \resumeItem{Solved problems in number theory, game theory, and calculus.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Synvo Chatbot}}{Feb 2025 -- Present}
          \resumeItemListStart
            \resumeItem{A chatbot with multimodal memory.}
            \resumeItem{Completed the project's RAG system, along with its frontend and backend.}
            \resumeItem{Assisted in the training of audio models, implementing the Direct Preference Optimization code for training.}
            \resumeItem{Founded a startup based on this project and raised \$4M USD in an angel round.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{LMMs-Eval}}{Jan 2024 -- Present}
          \resumeItemListStart
            \resumeItem{Open-source evaluation frameworks spanning text, image, video, and audio tasks with 2.6K GitHub stars.}
            \resumeItem{Contributed to the pipeline code and developed Multi-modal LiveBench.}
            \resumeItem{Adopted by projects such as \href{https://llava-vl.github.io/blog/2024-08-05-llava-onevision/}{LLaVA} (ByteDance) and \href{https://apollo-lmms.github.io/}{Apollo} (Meta).}
            \resumeItem{Paper accepted by NAACL (Findings), first co-author.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Video-MMMU}}{Sep 2024 -- Feb 2025}
          \resumeItemListStart
            \resumeItem{Built an evaluation set on multi-discipline professional videos.}
            \resumeItem{Contributed to algorithms for evaluating model learning capabilities.}
            \resumeItem{Evaluated LMMs' knowledge acquisition on videos.}
            \resumeItem{Project cited by \href{https://deepmind.google/models/gemini/pro/}{Gemini 2.5 Pro} (Google), \href{https://arxiv.org/pdf/2505.07062}{Seed1.5-VL} (ByteDance) and \href{https://arxiv.org/abs/2504.07491}{Kimi-VL} (Moonshot AI).}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Multi-Modal In-Context Instruction Tuning (Otter, MIMIC-IT)}}{Jun 2023 -- Dec 2023}
          \resumeItemListStart
            \resumeItem{Early experiment on a vision-language-agent (VLA) model with RLHF.}
            \resumeItem{Developed a pipeline to generate a multimodal instruction tuning dataset using pure language models.}
            \resumeItem{Paper accepted by \textit{IEEE Transactions on Pattern Analysis and Machine Intelligence} (TPAMI), first co-author.}
            \resumeItem{Earned 3.3k stars on GitHub.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

\section{Skills}

\textbf{Software Development}: Python (FastAPI, Celery, Gradio), C/C++, Java (Spring Boot), Golang (gRPC), JavaScript/TypeScript (React), HTML, MongoDB, SQL (SQLite, PostgreSQL)

\textbf{Model Training}: PyTorch, Hugging Face (Transformers, Datasets, PEFT, Accelerate)

\textbf{Mathematical Programming}: Lean, R, Matlab, Julia

\textbf{Tools}: Git, \LaTeX, Typst, Markdown

\textbf{Languages}: English, Chinese, Japanese

\section{Activities}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Nanyang Programming Contest}{Jan 2025 -- Present}
      {Nanyang Technological University}{Singapore}
      \resumeItemListStart
        \resumeItem{Organized 2 competitions and tutorials to non-ICPC students.}
        \resumeItem{Aimed at helping students struggling with algorithm problems in interviews.}
      \resumeItemListEnd

    \resumeSubheading
      {NTU Students' Computing and Data Science Club}{Nov 2024 -- Present}
      {Nanyang Technological University}{Singapore}
      \resumeItemListStart
        \resumeItem{Managed a telegram group with 130+ members.}
        \resumeItem{Answer questions about AI/ML and share learning resources related to AI/ML.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Hobbies}

Chess (lichess rating: 2084), calligraphy, table tennis

\section{Services}

\textbf{Reviewer}: TMM, ACL

%-------------------------------------------
\end{document}
